\documentclass[article,8pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{listings}                   %for spacing.
\usepackage{enumitem}% http://ctan.org/pkg/enumitem

\geometry{left=2.0cm, top=1.5cm, right=2.0cm, bottom=2.0cm, footskip=.5cm}
\setlist[itemize]{topsep=0em, noitemsep}


% Bulletpoints do not show up in main text

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{1pt}{1pt} % Spacing around sections
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr5]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge Andrew Matsumoto}
	\bigskip\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
\section{Personal Data}

\begin{tabular}{rl}
    \textsc{Address:}   & 3407 E Kachina Dr., Phoenix, AZ 85044\\
    \textsc{Phone:}     & (480) 636-6490\\
    \textsc{email:}     & \href{mailto:arm297@cornell.edu}{arm297@cornell.edu}
\end{tabular}

%Section: Education
\section{Education}
\textbf{Masters of Engineering, Cornell University, Computer Science}, Ithaca, NY 2017-2018\\
\hspace*{1em}\textsc{GPA}: 3.51\\
\hspace*{1em}\textsc{Key Courses}: Parallel Computing, Distributed Computing, Constructive Type Theory, Compilers\\
\hspace*{1em}Machine Learning for Data Science, Machine Learning for Intelligent Systems
\\\\
\textbf{Bachelors of Science, Cornell University, Computer Science}, Ithaca, NY 2013-2017\\
\hspace*{1em}Graduated \textit{cum laude}\\
\hspace*{1em}\textsc{GPA}: 3.63\\
\hspace*{1em}\textsc{Key Courses}: Analysis of Algorithms, Operating Systems, Functional Programming, Theory of Computing,\\
\hspace*{1em}Artificial Intelligence, Computer Vision, Discrete Structures, Robotics, Programming Languages and Logic,\\
\hspace*{1em}Object Oriented Programming
%Section: Work Experience at the top
\section{Work Experience}
\textbf{The Boeing Company, Cybersecurity Software Engineering Intern (Summer 2016)}
\vspace{-0.5em}
\begin{itemize}
    \item Analyzed and classified traffic flow packets captured during flights.
    \item Developed software to find and extract malicious software packets.
\end{itemize}\\
\textbf{Argon ST, Software Engineering Intern (Summer 2015)}
\vspace{-0.5em}
\begin{itemize}
    \item Developed UI for displaying system information for naval fleet.
    \item Developed software solutions focused on web design and Internet security.
    \item Worked on team refactoring source code for the tactical operating display.
\end{itemize}\\
\textbf{Cornell University, Teaching Assistant (2015-2016, 2018)}
\vspace{-0.5em}
\begin{itemize}
    \item Object-Oriented Programming and Data Structures (CS 2110)
    \item Lead recitation teaching students object-oriented programming concepts and applications.
    \item Created questions for and proctored student exams.
\end{itemize}

%Section: Projects
\section{Key Projects}
\textbf{Cornell University Game Library (2018)}
\vspace{-0.5em}
\begin{itemize}
    \item Designed and implemented behavior tree module to game engine for use in CS 4152 (Advanced Topics in Computer Game Development).
\end{itemize}\\
\textbf{Engineering to Save the World (2018)}
\vspace{-0.5em}
\begin{itemize}
    \item A game application to educate engineers and students on system engineering concepts.
    \item Developed architecture and UI for mini-games drills.
    \item Reorganized project and maintained GitHub repository.
\end{itemize}

\section{Applicable Skills}
\textbf{Programming Languages}\\
\begin{tabular}{lp{15cm}}
Proficient:&C/C++, Java, Python, C\#, OCaml, LaTeX\\
Familiar:&MySQL, MATLAB, Julia, Markdown\\
\end{tabular}
\textbf{Operating Systems}:\\
\begin{tabular}{lp{15cm}}
Proficient:& Windows (7,8,10)\\
Familiar:&CentOS\\
\end{tabular}
\textbf{Software}:\\
\begin{tabular}{lp{15cm}}
Proficient:&Git, Vim, Visual Studio, Eclipse, NumPy, SciPy\\
Familiar:&OpenMP, MPI, JFlex, JavaCUP, GDB, Valgrind, Unity3D\\
\end{tabular}
\newpage
\section{Awards/Certificates}
\textbf{Dean's List (Spring 2014-Fall 2015, Fall 2016)}\\
\textbf{John McMullen Dean's Scholar (2013)}\\
\textbf{National Merit Finalist (2013)}\\

%\XeTeXpdffile ''GMAT.pdf'' page 1 scaled 800

\end{document}
